### 2021-10-19 documentos/vector_space.tex
Estoy atorado en el paso al oplus

Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$\janote{Qué es $\Omega$?}, as each member of the sum \janote{is}
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:2N} from 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$\janote{la resta no es al revés?}
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection.

>>>>

Other two simple but crucial
observation are the following. For valid quantum channels, 
% \begin{equation}
% % \sum_{
% \end{equation}
$\sum_{\valpha \in \Omega} \lambda_\valpha=0$ implies that 
$\lambda_\valpha=0$ for all $\valpha\in \Omega$\janote{Qué es $\Omega$?}, as each member of the sum \janote{is}
greater or equal to zero, 
% $p_{\vec\alpha}+p_{\vec\beta}=0$ implies $p_{\vec\alpha}=p_{\vec\beta}=0$, as
% all $p_{\vec\alpha} \ge 0$
due to complete positivity of the underlying channel. 
Finally, looking into the first component of \eref{eq:tau:is:A:p}, and taking into 
account the normalization condition that $\tau_{\vec 0}=1$, we obtain
\begin{equation}
\sum_\valpha \lambda_\valpha = 2^N,
\label{eq:sum:alpha:is:2N}
\end{equation}
since, $A_{\vec 0, \vbeta}=1$ for all $\vbeta$. \par
% }}}
% Conexion de los indices para llegar al grupo de Klein {{{
Now we need a definition: to each multi-index $\vec\alpha$ we associate a \textit{set}
of multi-indices $\Phi(\vec\alpha)$ as follows
\begin{equation}
\Phi(\vec\alpha):=\left\{
\vec\beta:\san_{\vec\alpha\vec\beta}=1
\right\}
% =\left\{ \vec\beta: \sa_{\alpha_1\beta_1}\cdot\ldots\cdot \sa_{\alpha_N\beta_N}
% =1
% \right\}
\label{eq:8}
\end{equation}
If we now assume that $\tau_{\vec\alpha}=1$, it follows from subtracting 
\eref{eq:sum:alpha:is:2N} from 
$\sum_{\vec\beta}\san_{\vec\alpha\vec\beta}\lambda_{\vec\beta}=2^N$\janote{la resta no es al revés?}
(which follows from the aforementioned assumption), 
% \begin{subequations}
% \begin{eqnarray}
% \sum_{\vec\beta}p_{\vec\beta}&=&1
% \label{eq:9a}\\
% \sum_{\vec\beta}\san_{\vec\alpha\vec\beta}p_{\vec\beta}&=&\tau_{\vec\alpha}=1
% \end{eqnarray}
% \label{eq:9}
% \end{subequations}
% that for all $\vec\beta\notin\Phi(\vec\alpha)$
\begin{eqnarray}
\lambda_{\vec\beta}=0,\quad \forall \vec\beta\notin\Phi(\vec\alpha).
\label{eq:condition:lambda:zero:Phi}
\end{eqnarray}
Thus, if $\tau_{\vec\alpha}=1$, then $\tau_{\vec\gamma}$
and $\tau_{\vec{\gamma^\prime}}$ are equal if
% , for all $\vec\beta\in\Phi(\vec\alpha)$.
\begin{equation}
\san_{\vbeta\vec\gamma}=\san_{\vbeta\vec{\gamma^\prime}}, \quad
\forall \vec\beta\in\Phi(\vec\alpha).
\label{eq:coneccion:dos:indices:A}
\end{equation}
% holds for all $\vec\beta\in\Phi(\vec\alpha)$. 
This follows from restricting the sum \eref{eq:tau:is:A:p}
to the $\lambda_\vbeta \ne 0$, given in \eref{eq:condition:lambda:zero:Phi}. 
\janote{Para entender esto tuve que revisar de nuevo 
el manuscrito de Francois. No veía cómo llegar a la implicación establecida
en \eqref{eq:coneccion:dos:indices:A}. Creo que algunos pasos intermedios son
importantes.}
Condition (\ref{eq:coneccion:dos:indices:A}) therefore connects three multi-indices, $\vec\alpha$,
$\vec\gamma$ and $\vec{\gamma^\prime}$.
When such a connection exists, $\tau_{\vec\alpha}=1$ implies
$\tau_{\vec\gamma}=\tau_{\vec{\gamma^\prime}}$. Let us now work out the nature
of this connection.
